---
title: "Epiviz Widgets"
author: "Hector Corrada Bravo"
date: "June 1, 2015"
output: 
  html_document:
    theme: default
---

```{r options, echo=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

This is a prototype of embedding epiviz JS visualizations on Rmarkdown using the `epivizWidgets` package.
This infrastructure is built on `htmlwidgets`.

Plotting an `ExpressionSet`. Compute average for tumor and normal, then make an MA plot. 

```{r pkgs, message=FALSE}
require(epivizr)
require(antiProfilesData)

data(apColonData)
```

```{r setup}
keep <- pData(apColonData)$SubType!="adenoma"
apColonData <- apColonData[,keep]
status <- pData(apColonData)$Status
Indexes <- split(seq(along=status),status)

exprMat <- exprs(apColonData)
mns <- sapply(Indexes, function(ind) rowMeans(exprMat[,ind]))
mat <- cbind(colonM=mns[,"1"]-mns[,"0"], colonA=0.5*(mns[,"1"]+mns[,"0"]))
assayDataElement(apColonData, "MA") <- mat
show(apColonData)
```

This is how it's used. `apColonData` is an `ExpressionSet`, `columns` specify which columns in assay `MA` are going to be plotted.

```{r scatterplot, cache=FALSE}
library(epivizWidgets)
epivizWidgets::scatterplot(apColonData, columns=c("colonA","colonM"), assay="MA")
```

TODO: 

- add epiviz decorations (tool-tips, settings dialogs).  
- fix issue with CSS styles  

More advanced TODO: 

- use the epiviz event infrastructure to implement highlight-on-hover.  

